---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ozdates

[![Travis build status](https://travis-ci.org/deanmarchiori/ozdates.svg?branch=master)](https://travis-ci.org/deanmarchiori/ozdates)   ![](https://img.shields.io/badge/lifecycle-experimental-orange.svg) 

The goal of `ozdates` is to provide historical data of important Australian dates to help with data analysis and time series modelling.  

Current features:  

* `aus_public_holidays`: Australian Public Holidays Dates Machine Readable Dataset 2014-2019 - transformed into tidy format. (Source: https://data.gov.au/dataset/australian-holidays-machine-readable-dataset)  

* `aus_daylight_saving`: Historical start and end time of Australian daylight saving time dates according to the Australian Bureau of Meteorology. (Source: http://www.bom.gov.au/climate/averages/tables/dst_times.shtml)  

## Installation

You can install the development version of ozdates from [Github](https://github.com/deanmarchiori/ozdates) with:

``` r
devtools::install_github("deanmarchiori/ozdates")
```

## Examples

Some basic examples:  

### Public Holidays

```{r example_pubhol, message=FALSE, warning=FALSE}
library(ozdates)
library(dplyr)
library(lubridate)

# What holidays occured in New South Wales in 2018?
nsw_hols <- aus_public_holidays %>% 
  filter(jurisdiction == "NSW",
         year(date) == "2018") %>% 
  select(date, holiday_name, jurisdiction)

nsw_hols

# Are there any public holidays in the next 2 months?
any(nsw_hols$date %within% interval(ymd("2018-04-01"), ymd("2018-05-30")))
```

### Daylight Saving Time  

```{r example_dst, message=FALSE, warning=FALSE}
library(ozdates)
library(dplyr)
library(lubridate)

# Which states participate in DST in 2017 and on what dates?
aus_daylight_saving %>% 
  filter(season_start == 2017)

```

-----

Please note that the 'ozdates' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.     

The use of data in this package must conform with the licence conditions it was published under. See data documentation for licence and copyright information.   

While care is taken when transforming and representing data. No responsibility is taken for inaccuracies or loss arising from the use of this software and data. See the [LICENSE](LICENSE.md) for more information.  

