---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ozdates

[![Travis build status](https://travis-ci.org/deanmarchiori/ozdates.svg?branch=master)](https://travis-ci.org/deanmarchiori/ozdates)   ![](https://img.shields.io/badge/lifecycle-experimental-orange.svg) 

The goal of `ozdates` is to provide historical data of important Australian dates to help with data analysis and time series modelling.  

Current features:  

* `aus_public_holidays`: Australian Public Holidays Dates Machine Readable Dataset - tranformed into tidy format. (Source: https://data.gov.au/dataset/australian-holidays-machine-readable-dataset)

## Installation

You can install the development version of ozdates from [Github](https://github.com/deanmarchiori/ozdates) with:

``` r
devtools::install_github("deanmarchiori/ozdates")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE, warning=FALSE}
library(ozdates)
library(dplyr)
library(lubridate)

# What holidays occured in New South Wales in 2018?
nsw_hols <- aus_public_holidays %>% 
  filter(jurisdiction == "NSW",
         year(date) == "2018") %>% 
  select(date, holiday_name, jurisdiction)

nsw_hols

# Are there any public holidays in the next 2 months?
any(nsw_hols$date %within% interval(ymd("2018-04-01"), ymd("2018-05-30")))
```


-----

Please note that the 'ozdates' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.    

The use of data in this package must conform with the licence conditions it was published under. See [Creative Commons Attribution 3.0 Australia](https://creativecommons.org/licenses/by/3.0/au/)

